---
title: "Example R Markdown Demo"
author: "Joey Lipoff"
date: "June 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment examines the features of [RMarkdown](http://www.rstudio.org/docs/authoring/using_markdown) using [knitr](http://yihui.name/knitr/) in Rstudio.  

## Getting started
To work with R Markdown, if necessary:\Install R.
Install the lastest version of RStudio.
Install the latest version of the knitr package: install.packages("knitr").

To run the basic working example that produced this blog post:
Open R Studio, and go to File - New - R Markdown
If necessary install ggplot2 and lattice packages: install.packages("ggplot2"); install.packages("lattice")
Save the file with an .rmd extension.
Write your source code.
Click Knit HTML to view the document in real time-you can do this repeatedly to see how your changes are implemented.

## Prepare for analyses
I've written a chunk of R code here to set my seed and load the necessary packages. **Note:** these packages have to already be installed on your machine or the `library()` command will give you an error message. My warning below is because I have an older version of R running on my machine.

```{r }
set.seed(1234)
library(ggplot2)
library(lattice)
```

## Basic console output
```{r}
x <- 1:10
y <- round(rnorm(10,x, 1),2)
df<- data.frame
df
```


## Plots
Images generated by knitr are saved in a figures folder. However, they also appear to be represented in the HTML output using a data URI scheme. This means that you can paste the HTML into a blog post or discussion forum and you don't have to worry about finding a place to store the images; they're embedded in the HTML.

### Simple plot
plot(x)

### Multiple plots
You can include multiple plots in one code chunk. Below, what appears to be two separate chunks is actually one chunk with two plots-the first line is the boxplot() command and the second line is the plot() command:

Boxplot
```{r}
boxplot(1:10~rep(1:2,5))
```

Plot
```{r}
plot(x,y)
```


### `ggplot2` plot
ggplot2 plots work well. We'll learn much more about these soon:
```{r}
qplot(x,y, df)
```


### `lattice` plot
As do lattice plots:
```{r}
xyplot(y~x)
```


## R Code chunk features
### Control output display
Code chunk options including echo = and comment = control the display of the R code and comments, respectively, in the HTML report. Typing echo=FALSE will prevent the code from being printed about its output. Typing comment="" will suppress all text from the console output (e.g., warnings, etc.). You can't see the code chunk that produced the output below because I've typed echo=FALSE into it. However, I simply asked for the first six rows of df using head(df).

  x     y
1 1 -0.21
2 2  2.28
3 3  4.08
4 4  1.65
5 5  5.43
6 6  6.51

### Control figure size
The following is an example of a smaller figure using fig.width and fig.height chunk options. Here, I typed fig.width=3, fig.height=3 in the chunk options.
```{r}
plot(x)
```

## Basic markdown functionality
For those not familiar with standard Markdown, the following may be useful. See the RMarkdown cheatsheet for how to produce such points. You can access it directly from the RStudio Help menu.

### Dot Points
Simple dot points:
Point 1
Point 2
Point 3
and numeric dot points:
Number 1
Number 2
Number 3
and nested dot points:
A 
A.1
A.2
B 
B.1
B.2

### Equations
Equations are included by using LaTeX notation and including them either between single dollar signs (inline equations) or double dollar signs (displayed equations).
If you hang around the Q&A site [CrossValidated](http://stats.stackexchange.com) you'll be familiar with this idea.

There are inline equations such as $y_i = \alpha + \beta x_i + e_i$.



### Tables
Tables can be included using relatively simple typesetting:
A        B      C
1      Male    Red
2      Female  Orange


### Hyperlinks
If you like torture, learn more about LaTex typesetting here.

### Code
R inline code such as x <- 1:10 can also be used.

### Quote
Let's quote some stuff. Bonus points if you know Who said it.
  #The truth. It is a beautiful and terrible thing, and should therefore be treated with caution.
## Conclusion
* R Markdown is awesome. 
    * The ratio of markup to content is excellent. 
* The RStudio team have made the whole process very user friendly.
    * RStudio provides useful shortcut keys for compiling to HTML, and running code chunks. 
    * The formula and table support are particularly useful.
    * Jump-to-chunk feature facilitates navigation. It helps if your code chunks have informative names.
    * Code completion on R code chunk options is really helpful. See also [chunk options documentation on the knitr website](http://yihui.name/knitr/options).
* Other recent posts on R markdown include those by :
     * [Christopher Gandrud](http://christophergandrud.blogspot.com.au/2012/05/dynamic-content-with-rstudio-markdown.html)
     * [Markcus Gesmann](http://lamages.blogspot.com.au/2012/05/interactive-reports-in-r-with-knitr-and.html)
     * [Rstudio on R Markdown](http://rstudio.org/docs/authoring/using_markdown)
     * [Yihui Xie](http://yihui.name/knitr/): developed `knitr`. He has also posted [this example of R Markdown](https://github.com/yihui/knitr/blob/master/inst/examples/knitr-minimal.Rmd).

## Document Information.

All of the statistical analyses in this document will be performed using `r R.version.string`.  R packages used will be maintained using the [packrat](http://rstudio.github.io/packrat/) dependency management system.  

```{r session-info}
sessionInfo()
```
